Response to the defense feedback

### 2021-06-02 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation. Prof. Liu and Prof. Zhu greatly improved this dissertation with their comments from a security research angle. Prof. Hanrahan and Prof. Larus helped me improve the grammar of my dissertation. Jim is my last English teacher. I learned a lot on the written English from him.  His comments are also very close to what I get from reviewers later. However, I did not take his comments seriously at the very beginning.

>>>>

The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation. Prof. Liu and Prof. Zhu greatly improved this dissertation with their comments from a security research angle. Prof. Hanrahan helped me improve the grammar of my dissertation proposal and my dissertation. Prof. Larus is a senior researcher and my last English teacher. I learned a lot on the written English from him.  His comments on the early draft are also very close to what I got from reviewers later. However, I did not take his comments seriously at the very beginning.
